\documentclass[journal,12pt,twocolumn]{IEEEtran}
\usepackage{amsmath}
\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
\title{ Assignment1}
\author{PARIMISETTY HARINADHA (CS19RESCH11004)}
\begin{document}
\maketitle
\newpage
\begin{abstract}
This document explains the concept of collinear and whether the triangle formed by given 3 points is right angled triangle or not.
\end{abstract}
Download all python codes from 
\framebox[1\width]{ https://github.com/cs19resch11004/5600/hari } \\
\newline
Download all Latex-tikz codes from 
\framebox[1.1\width]{ https://github.com/cs19resch11004/5600/hari} 
\section{Problem}
Without using the Pythagoras theorem, show that \myvec{ 4 \\ 4 }, \myvec{ 3 \\ 5 } and \myvec{ -1 \\ -1 } are the vertices of a right angled triangle?
\section{Explanation}
Initially we will test whether given 3 points are collinear or not. If they are non-collinear then we will check whether the triangle formed by given 3 points is right angled triangle or not by using one of the follwing 2 methods. \\
1. Direction vector based method\\
2. Slope method\\
In this document we are going to use Direction vector based method.\\
	Let A, B and C are 3 non-collinear points, then we will test, whether any two of the following Direction vectors $\vec{AB}$ and $\vec{AC}$ or $\vec{AB}$ and $\vec{BC}$ or $\vec{AC}$ and $\vec{BC}$ are perpendicular to each other or not by using DOT PRODUCT.
\\
\section{Solution}
The direction vectors of AB, AC and BC are
$\\
	\vec{AB}=\myvec{-1 \\ 1} \\
	\vec{AC}=\myvec{-5 \\ -5}\\
	\vec{BC}=\myvec{-4 \\ -6} 
$
\\
\\
\\
Testing of  $\vec{AB}$ and $\vec{BC}$ are perpendicular to each other or not?\\
DOT PRODUCT of  $\vec{AB}$ and $\vec{BC}$ is, \begin{align} \myvec{ -1 \\ 1 } ^ {T} . \myvec{ -4 \\ -6 } = -2\end{align}\\
$\vec{AB}$ . $\vec{BC}$ = -2 $\neq$ 0 \\
Sides AB and BC of triangle are not perpendicular.
\\
\\
\\
Testing of  $\vec{AC}$ and $\vec{BC}$ are perpendicular to each other or not?\\
DOT PRODUCT of  $\vec{AC}$ and $\vec{BC}$ is, \begin{align} \myvec{ -5 \\ -5 } ^ {T} . \myvec{ -4 \\ -6 } = 50\end{align}\\
$\vec{AC}$ . $\vec{BC}$ = 50 $\neq$ 0 \\
Sides AC and BC of triangle are not perpendicular.
\\
\\
\\
Testing of  $\vec{AB}$ and $\vec{AC}$ are perpendicular to each other or not?\\
DOT PRODUCT of  $\vec{AB}$ and $\vec{AC}$ is, \begin{align} \myvec{ -1 \\ 1 } ^ {T} . \myvec{ -5 \\ -5 } = 0\end{align}\\
$\vec{AB}$ . $\vec{AC}$, which is 0 \\
Sides AB and AC of triangle are perpendicular to each other. So Triangle ABC is right angled triangle and right angle at vertex \myvec{ 4 \\ 4 }.  
\end{document}
